### 2022-04-06 tables/rep_table_3b.tex
edits to table 3 output

\begin{table}[htbp]
   \caption{\label{tab:replicatetable3a} Replication of Table 3 Panel A : Fixed Effects Regressions}
   \centering
   \small
   \begin{tabular}{lccc}
      \tabularnewline \midrule \midrule
      Dependent Variables:     & violent\_crime\_rate\_log    & property\_crime\_rate\_log    & murder\_crime\_rate\_log\\     
      Model:                   & (1)                          & (2)                           & (3)\\  
      \midrule
      \emph{Variables}\\
      shalll                   & -0.0978$^{***}$              & -0.0072                       & -0.0507\\   
                               & (0.0324)                     & (0.0194)                      & (0.0394)\\   
      Relevant\_Arrest\_Rate   & -0.0003                      & -0.0020$^{*}$                 & -0.0004\\   
                               & (0.0004)                     & (0.0011)                      & (0.0002)\\   
      \midrule
      \emph{Fixed-effects}\\
      state                    & Yes                          & Yes                           & Yes\\  
      year                     & Yes                          & Yes                           & Yes\\  
      \midrule
      \emph{Fit statistics}\\
      Observations             & 802                          & 809                           & 806\\  
      R$^2$                    & 0.98146                      & 0.96445                       & 0.94792\\  
      Within R$^2$             & 0.47334                      & 0.55426                       & 0.31137\\  
      \midrule \midrule
      \multicolumn{4}{l}{\emph{Clustered (state) standard-errors in parentheses}}\\
      \multicolumn{4}{l}{\emph{Signif. Codes: ***: 0.01, **: 0.05, *: 0.1}}\\
   \end{tabular}

>>>>

\begin{table}[htbp]
   \caption{\label{tab:replicatetable3b} Replication of Table 3 Panel B : Fixed Effects Regressions}
   \centering
   \small
   \begin{tabular}{lccc}
      \tabularnewline \midrule \midrule
      Dependent Variables:     & rape\_crime\_rate\_log    & assault\_crime\_rate\_log    & robbery\_crime\_rate\_log\\     
      Model:                   & (1)                       & (2)                          & (3)\\  
      \midrule
      \emph{Variables}\\
      shalll                   & -0.0340                   & -0.1004$^{**}$               & -0.0532\\   
                               & (0.0395)                  & (0.0424)                     & (0.0439)\\   
      Relevant\_Arrest\_Rate   & -0.0006                   & -0.0028$^{***}$              & -0.0014\\   
                               & (0.0005)                  & (0.0009)                     & (0.0009)\\   
      \midrule
      \emph{Fixed-effects}\\
      state                    & Yes                       & Yes                          & Yes\\  
      year                     & Yes                       & Yes                          & Yes\\  
      \midrule
      \emph{Fit statistics}\\
      Observations             & 799                       & 809                          & 808\\  
      R$^2$                    & 0.94240                   & 0.96632                      & 0.98389\\  
      Within R$^2$             & 0.52351                   & 0.51645                      & 0.50471\\  
      \midrule \midrule
      \multicolumn{4}{l}{\emph{Clustered (state) standard-errors in parentheses}}\\
      \multicolumn{4}{l}{\emph{Signif. Codes: ***: 0.01, **: 0.05, *: 0.1}}\\
   \end{tabular}

### 2022-04-06 tables/rep_table_3c.tex
edits to table 3 output

\begin{table}[htbp]
   \caption{\label{tab:replicatetable3b} Replication of Table 3 Panel B : Fixed Effects Regressions}
   \centering
   \small
   \begin{tabular}{lccc}
      \tabularnewline \midrule \midrule
      Dependent Variables:     & rape\_crime\_rate\_log    & assault\_crime\_rate\_log    & robbery\_crime\_rate\_log\\     
      Model:                   & (1)                       & (2)                          & (3)\\  
      \midrule
      \emph{Variables}\\
      shalll                   & -0.0340                   & -0.1004$^{**}$               & -0.0532\\   
                               & (0.0395)                  & (0.0424)                     & (0.0439)\\   
      Relevant\_Arrest\_Rate   & -0.0006                   & -0.0028$^{***}$              & -0.0014\\   
                               & (0.0005)                  & (0.0009)                     & (0.0009)\\   
      \midrule
      \emph{Fixed-effects}\\
      state                    & Yes                       & Yes                          & Yes\\  
      year                     & Yes                       & Yes                          & Yes\\  
      \midrule
      \emph{Fit statistics}\\
      Observations             & 799                       & 809                          & 808\\  
      R$^2$                    & 0.94240                   & 0.96632                      & 0.98389\\  
      Within R$^2$             & 0.52351                   & 0.51645                      & 0.50471\\  
      \midrule \midrule
      \multicolumn{4}{l}{\emph{Clustered (state) standard-errors in parentheses}}\\
      \multicolumn{4}{l}{\emph{Signif. Codes: ***: 0.01, **: 0.05, *: 0.1}}\\
   \end{tabular}

>>>>

\begin{table}[htbp]
   \caption{\label{tab:replicatetable3c} Replication of Table 3 Panel C : Fixed Effects Regressions}
   \centering
   \small
   \begin{tabular}{lccc}
      \tabularnewline \midrule \midrule
      Dependent Variables:     & burglary\_crime\_rate\_log    & larceny\_crime\_rate\_log    & autotheft\_crime\_rate\_log\\     
      Model:                   & (1)                           & (2)                          & (3)\\  
      \midrule
      \emph{Variables}\\
      shalll                   & -0.0461$^{*}$                 & 0.0033                       & -0.0090\\   
                               & (0.0242)                      & (0.0206)                     & (0.0382)\\   
      Relevant\_Arrest\_Rate   & -0.0052$^{***}$               & -0.0011                      & -0.0003$^{*}$\\   
                               & (0.0018)                      & (0.0010)                     & (0.0002)\\   
      \midrule
      \emph{Fixed-effects}\\
      state                    & Yes                           & Yes                          & Yes\\  
      year                     & Yes                           & Yes                          & Yes\\  
      \midrule
      \emph{Fit statistics}\\
      Observations             & 809                           & 809                          & 808\\  
      R$^2$                    & 0.95597                       & 0.96600                      & 0.96116\\  
      Within R$^2$             & 0.50429                       & 0.54529                      & 0.60312\\  
      \midrule \midrule
      \multicolumn{4}{l}{\emph{Clustered (state) standard-errors in parentheses}}\\
      \multicolumn{4}{l}{\emph{Signif. Codes: ***: 0.01, **: 0.05, *: 0.1}}\\
   \end{tabular}
